\textit{Summary} 

The purpose of this document is to write about the environmental health course I am going to teach at the UC HLTH214. All course materials, thoughts, reflections, and lessons will be stored here. The ambition is that, in course of time, this wiil develop in the form of a book or text. 

\subsection{Idea for assessment}

This is going to be in the format of flipped classroom. I shall take videos of all my lessons (need to discuss with Rob Stowell) and upload the papers
Students will need to read these in advance, and then come prepared to discuss these in class.
Each week, will have five or six questions and meeting agenda posted o the learn site

On the first day of he class at the end of the class the students will be given this asssignment:
\begin{enumerate}
\item Each student will use his or her phone camera or another digital camera to photograph her environment.
\item In the next class, he will be prepared to walk us through his experience of phhotographing his or her environment, and occupations if that is the case
\item Based on those photographs and interpretations, we shall develop plans for assessment. He will develop a topic that will be investigated in the end. 
\item First assignment, photograph community or occupation and write about it.
\item Second assessment, multiple choice examination
\item Third assessment, final report on the problem studied

\end{enumerate}

We shall provide all the needed tools for this course and preparatory work. 

  